---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: theme/crmda-boilerplate.tex
    pandoc_args: [
      "--listings"
    ]
fontsize: 11pt
tables: true
preamble:
- \usepackage{xcolor}

title: "Title of this Document"
subtitle: "A Subtitle that may Flow onto Additional Space if Necessary"
author:
- name: Paul Johnson 
  affiliation: CRMDA
  description: Director
  email: crmda@ku.edu
- name:  Brent Kaplan 
  affiliation: CRMDA
  description: GRA
  email: crmda@ku.edu
---

```{r setup, include=FALSE}
##This Invisible Chunk is required in all CRMDA documents
tmpdir <- paste0("tmpout")
if (!dir.exists(tmpdir)) dir.create(tmpdir, recursive = TRUE)
knitr::opts_chunk$set(echo=TRUE, comment=NA, fig.path=paste0(tmpdir, "/p-"))
options(width = 70)
```


# Nuts and Bolts

## DO NOT change the top part.

Leave the "output" section, font size, and that LaTeX stuff

```
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: crmda-boilerplate.tex
    pandoc_args: [
      "--listings"
    ]
fontsize: 11pt
tables: true
preamble:
- \usepackage{xcolor}
- \usepackage{lipsum}    
```

This is pretty standard and you shouldn't change it. Some changes might
be needed if you *ADD* LaTeX preamble statements, but don't delete
the onese we have.

## DO please change Title, subtitle, your name

```
title: "My Fancy Rmd to PDF Document"
subtitle: "Made by yours truly!"
```
Include a title, a subtitle.

```
author:
- name: Paul Johnson
  affiliation: Center for Research Methods and Data Analysis
  description: Ze Director
  email: crmda@ku.edu
```

Someone's got to get credit for the wonderful report, right? If you're a graduate student, you can put that right in the description line. If you are not the CRMDA, then you might want to change the email line.


# LaTeX Syntax is allowed

## Equations

```
\[
\Sigma_{gt}=\Lambda_{gt}\Psi_{gt}\Lambda'_{gt}+\Theta_{gt}
\]
```

produces:

\[
\Sigma_{gt}=\Lambda_{gt}\Psi_{gt}\Lambda'_{gt}+\Theta_{gt}
\]

```
\[
f(y|N,p) = \frac{N!}{y!(N-y)!}\cdot p^y \cdot (1-p)^{N-y} = {{N}\choose{y}} \cdot p^y \cdot (1-p)^{N-y}
\]
```

produces:

\[
f(y|N,p) = \frac{N!}{y!(N-y)!}\cdot p^y \cdot (1-p)^{N-y} = {{N}\choose{y}} \cdot p^y \cdot (1-p)^{N-y}
\]

```
$\hat{y}=\beta_{0}+\beta_{2}x_{i}+\beta_{3}+x_{j}+\varepsilon_{ij}$
```

produces:

$\hat{y}=\beta_{0}+\beta_{2}x_{i}+\beta_{3}+x_{j}+\varepsilon_{ij}$

## ```R``` code 

```{r ex-1, results='asis', echo=TRUE}
## This can be changed in the .tex preamble under lstset
set.seed(1234)
x <- rnorm(100, 0, 1)
y <- rnorm(100, 0, 1)
plot(x, y)
knitr::kable(head(data.frame(x, y)))
z <- "A Character String"
```

```{r, results='asis',message=F}
library(xtable)
print(xtable(head(data.frame(x,y))), comment=FALSE)
```

```{r, include=FALSE}
xtbout <- xtable(head(data.frame(x,y)))
print(xtbout, file = file.path(tmpdir, "xtabl.tex"),
      type = "latex", include.rownames = FALSE)
```

```{r, include=FALSE}
print(xtbout, file = file.path(tmpdir, "xtabl.html"),
      type = "html", include.rownames = FALSE)
```	

```{r}
library(rockchalk)
set.seed(2134234)
dat <- data.frame(x1 = rnorm(100), x2 = rnorm(100))
dat$y1 <- 30 + 5 * rnorm(100) + 3 * dat$x1 + 4 * dat$x2
dat$y2 <- rnorm(100) + 5 * dat$x2
m1 <- lm(y1 ~ x1, data = dat)
m2 <- lm(y1 ~ x2, data = dat)
m3 <- lm(y1 ~ x1 + x2, data = dat)
gm1 <- glm(y1 ~ x1, family = Gamma, data = dat)
```

```{r}
summary(gm1)
```


```{r, results="asis"}
outreg(list("Whichever" = m1, "Whatever" = m2),
       title = "Still have showAIC argument, as in previous versions",
       showAIC = TRUE, float = TRUE)   
```     

```{r, include=FALSE}
  o1 <- outreg(list("Whichever" = m1, "Whatever" = m2),
            showAIC = TRUE, float=FALSE)
  cat(o1, file = file.path(tmpdir, "outreg1.tex"))
```

\begin{center}
\input{"tmpout/outreg1.tex"}
\end{center}

Here's the question: Is this report stationary better than what we
had? 

Lets get a team vote.

By the way, in case you wanted to see a giant copy of the logo, lets
test the ability to insert a PDF graphic:

\includegraphics[width=4in]{"theme/CRMDA_logo"}
