---
output: 
  pdf_document:
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: theme/report-boilerplate.tex
    pandoc_args: [
      "--listings"
    ]
fontsize: 11pt
tables: true
preamble:
- \usepackage{xcolor}

title: "Title of this Document"
subtitle: "A Subtitle that may Flow onto Additional Space if Necessary"
author:
- name: Paul Johnson 
  affiliation: CRMDA
  description: Director
  email: crmda@ku.edu
- name:  Brent Kaplan 
  affiliation: CRMDA
  description: GRA
  email: crmda@ku.edu
---

```{r setup, include=FALSE}
##This Invisible Chunk is required in all CRMDA documents
tmpdir <- paste0("tmpout")
if (!dir.exists(tmpdir)) dir.create(tmpdir, recursive = TRUE)
knitr::opts_chunk$set(echo=TRUE, comment=NA, fig.path=paste0(tmpdir, "/p-"))
options(width = 70)
```


# Nuts and Bolts

## Minor header edits only

The header has a place to insert a title, subtitle, email
addresses. Do not change the `pdf_document` settings unless you want
to get serious.

## To compile this document

To compile, either start R and use the function `rmd2pdf` or use the
shell script that is in the same directory as the `Rmd` file.

Compiling the document will also produce an R file that is a "tangled"
version of the code chunks in the document.

## Document customization: essentials

The function `rmd2pdf` (same as the script) supplies settings,
including a \LaTeX template called "report-boilerplate.tex".  That
boilerplate is, by default, found in the package itself, NOT in the
theme folder that is provided with this document.  If you do
want to edit the theme boilerplate, then it is necessary to respecify
the document header.  If you edit theme/report-boilerplate.tex, then
insert this in the header, within the pdf_document section:

```
template: theme/report-boilerplate.tex
```

In addition, if you insert \LaTeX features that require packages
that are not currently in the report-boilerplate.tex, then those
packages can be inserted into the preamble by YAML header markup like
so:
>>>>>>> zr_branch

```
preamble:
-  \usepackage{xcolor}
-  \usepackage{amsmath}
-  \usepackage{amssymb}
-  \usepackage{fancybox}
```

That example has the package `amssymb` because some non-standard math
symbols were needed.

# For math, much \LaTeX\ Syntax is allowed

This is explained in the `crmda` package vignette `Rmarkdown`.

Use `\[` and `\[` for display equations:

\[
\Sigma_{gt}=\Lambda_{gt}\Psi_{gt}\Lambda'_{gt}+\Theta_{gt}
\]

Note that the preamble may need new packages if you
insert more \LaTeX\ functionality.

# `R` code chunks

As explained in the `crmda` vignette `code_chunks`, many 
options are avaiable for code chunks.

# Required footer

Reports do not have the R session replication information, generally 
speaking.  However, compiling the document will produce a
record-keeping file in which the session information is saved. This
will be in the current working directory.

```{r session, include=F}
zz <- "report-instructions-sessionInfo.Rout"
capture.output(warnings(), file = zz)
capture.output(sessionInfo(), file = zz, append = TRUE)
```
